\chapter{Bread}
\minitoc

\recipe[Made from wheat flour, water, yeast, and common salt. It may contain up to 2\% broad bean flour, up to 0.5\% soya flour, and up to 0.3\% wheat malt flour according to the `Decr\'et de Pain 1993`]{Baguette de Tradition}
\label{rec:bread-baguette}
\preptime{4-4.5 hours}
\cooktime{25-30 minutes}

\begin{ingreds}
	200g liquid leaven (2:2:1)
	8g fresh yeast
	1000g T65 flour (Viron)
	20g sea salt
	600g water

\end{ingreds}

\begin{method}[Ensure the water is free of chlorine or other antisteptic additives.]
Mix for 8min slow speed + 3mn fast speed

2h bulk fermentation at 23$^{\circ}$ Celsius (3h at 19-20$^{\circ}$ Celsius in cold weather may be necessary)

Fold + 30 mn bench rest

Divide and preshape into batons + 15 min bench rest

Shape into baguettes

45mn proofing on baker's couche

Bake 25-30 min at 260-265$^{\circ}$ Celsius (top and bottom heat, no fan)

Trasfer to cooling rack

\end {method}

\recipe[I often like to make this one because it is so simple.  I even prefer it to the miche from Poil\^ane.]{Miche}
\label{rec:bread-campagne}
\preptime{5 hours}
\cooktime{25 minutes}

\begin{ingreds}
	400 g sourdough starter
	1000g french T85 flour
	20g sea salt
	620g water
\end{ingreds}

\begin{method}[Ensure the water is free of chlorine or other antisteptic additives.]
Dissolve the sourdough starter in the water and add the flour and mix coarsely.

Add the dry yeast and salt.

Now knead the flour using the stretch and fold technique, gently making 4 folds  every 15 minutes for a total time of about 2 1/2 hours.

Prepare oven for hearth baking by adding a pan filled with lava rocks at the bottom and preheat the to the maximum temperature, usually \temp{250} or higher.

Let the dough rise for 1 - 1 1/2 hours, then divide into equal rectangles.

Rest for about 30 minutes, then shape the dough into baguette rolls and transfer each baguette to their 'couche'.

Leave to rise for 1 1/2 - 2 hours.

Pour a glass of water over the lava rocks, make the incisions into the dough and transfer into the oven.

Bake until deep golden,  usually 20 - 25 minutes at 240$^{\circ}$ Celsius

Transfer to cooling rack.

\end {method}

\recipe[Country loaf with nutty flavours]{Spelt Loaf}
\label{rec:spelt-loaf}
%\preptime{5 hours}
\cooktime{30 minutes}

\begin{ingreds}
	10\% Wholemeal Spelt flour
	50\% White Spelt flour
	40\% T85 flour
	15\% Leven
	70\% Water
	2.0\% Sea Salt

\end{ingreds}

\begin{method}[Ensure the water is free of chlorine or other antisteptic additives.]
Dissolve the sourdough starter in the water and add the flour and mix coarsely.

Let it autolyse for 3-4 hours.

Add the dry yeast and salt.

Now knead the flour using the stretch and fold technique, gently making 4 folds  every 15 minutes for a total time of about 2 1/2 hours.

Prepare oven for hearth baking by adding a pan filled with lava rocks at the bottom and preheat the to the maximum temperature, usually \temp{250} or higher.

Let the dough rise for 1 - 1 1/2 hours, then divide into equal rectangles.

Rest for about 30 minutes, then shape the dough into baguette rolls and transfer each baguette to their 'couche'.

Leave to rise for 1 1/2 - 2 hours.

Pour a glass of water over the lava rocks, make the incisions into the dough and transfer into the oven.

Bake until deep golden,  usually 20 - 25 minutes.

Transfer to cooling rack.

\end {method}

\recipe[Also known as PLF.  It is used in many 'vienoisseries' such as croissants or pain au chocolat]{P\^ate Lev\'ee Ferment\'ee}
\label{rec:baking-plf}
%\preptime{5 hours}
%\cooktime{30 minutes}

\begin{ingreds}
	50\% T65
	50\% Gruau
	1.8\% Sea Salt
	15\% Sugar
	4\% Fresh Yeast
	10\% Levain (optional)
	5\% Egg
	25\% Water
	25\% Milk
	50\% Beurre de Tourage
\end{ingreds}

\begin{method}[]

First weigh the flours, then the dry ingredients commencing with the salt.
Once done proceed with the liquids.

Knead for about 10 minutes (pate ferme batarde), shape into boule, cover and 
rest for 10 minutes to relax the dough.

Then shape into 20cm to 30cm rectangle.

Cover and cool in the fridge for 30 minutes.
\end {method}

\recipe[Makes 6 croissants]{Croissants}
\label{rec:baking-crossiant}
%\preptime{5 hours}
%\cooktime{30 minutes}

\begin{ingreds}
	84g T65
	84g Gruau
	3g Sea Salt
	25g Sugar
	6g Fresh Yeast
	17g Levain
	9g Egg
	42g Water
	42g Milk
	84g Beurre de Tourage
\end{ingreds}

\begin{method}[]
Proceed as for P\^ate Lev\'ee Ferment\'ee~(sec~\ref{rec:baking-plf}).

\end {method}

\recipe[Makes 6 Pains au chocolat]{Pains au Chocolat}
\label{rec:baking-pain-au-chocolat}
\preptime{5 hours}
\cooktime{14 minutes}

\begin{ingreds}
	84g T65
	84g Gruau
	3g Sea Salt
	25g Sugar
	6g Fresh Yeast
	17g Levain
	9g Egg
	42g Water
	42g Milk
	84g Beurre de Tourage
\end{ingreds}

\begin{method}[]
Proceed as for P\^ate Lev\'ee Ferment\'ee~(sec~\ref{rec:baking-plf}).

Shape the pastry as illustrated below.

Proof for 2-2.5 hours at about \temp{28}.

Cover with eggwash and bake at \temp{160} in a fan oven for approximately 14 minutes.

\showit[3.5in]{img/pain-au-chocolat-layout}{Layout the dough to fit the cocolat batons}

\showit[3.5in]{img/pain-au-chocolat-first-fold}{Insert the first chocolate baton and fold}

\showit[3.5in]{img/pain-au-chocolat-second-fold}{Insert the second chocolate baton and fold}

\showit[3.5in]{img/pain-au-chocolat-roll-and-close}{Roll and press to close shut}

\end {method}


\recipe[]{Napoletan Pizza Dough}
\label{rec:pizza-dough-napoletan}
\preptime{24 - 48 hours}

\begin{ingreds}
	70\% Water
	2.6\% Sea Salt
	0./3\% Instant Yeast
	100\% Flour, Type 00
\end{ingreds}

\recipe[]{Pizza Margherita}
\label{rec:pizza-margherita}

\begin{ingreds}
	180 - 250g Dough per pizza (see~\ref{rec:pizza-dough-napoletan})
	60 - 80g Basic Tomato Sauce
	Extra-Virgin Olive Oil 
	10 to 15g Pecorino Romano or Parmigiano Reggiano
	80 - 100g Mozzarella di bufala, sliced into strips
	3 to 5 fresh whole basil leaves
\end{ingreds}


\recipe[Makes one loaf of Brioche as it is taught in France for the CAP Boulanger exam.]{Brioche}
\label{rec:bread-brioche}

\begin{ingreds}
	500g Farine de Gruau (T45)
	10g Dry Yeast
	125g Eggs
	250g Milk
	100g Butter
	50g Sugar
	8g salt
\end{ingreds}

\begin{method}[]
	Mix and let it double in size in a warm place (oven at \temp{30} is fine).

	Degas and partition in three and shape into a bead.

	Line a bread tin with parchment paper, cover with cling film.
	
	Let the dough proof until it rises just towards the top end of the tin (about 15-20 minutes).

	Bake in fan oven at \temp{160} for 25 minutes.
\end{method}

