\chapter{Desserts}
\minitoc

\recipe[]{Cr\^epes}
\label{desserts:crepes}
\begin{ingreds}
    3 eggs
    300g plain flour
    150ml milk
    butter for frying
\end{ingreds}

\begin{method}
    Whisk together the eggs and flour.

    Add the milk to make a batter that will thinly coat the
    back of a spoon.  Be careful not to over whisk or the batter
    won't be light.

    Heat a pan, and when it is very hot, add a knob of butter.

    Using a ladle pour in enough batter to thinly coat the base of
    the pan.

    Cook until golden, then flip the pancake over and cook on the
    other side.

\end{method}

\recipe[]{Passion Fruit Trifle}
%\preptime{15 minutes}
%\cooktime{7-10 minutes}
\serves{6 persons}

\begin{ingreds}
	250g tub mascarpone
    50g golden caster sugar
    1 tsp vanilla extract
    300ml carton double cream
    9 passion fruits
    1 orange, juice only
    3 thick slice of brioche loaf or plain sponge cake
    3 mangoes, thinly sliced
\end{ingreds}

\begin{method}
    Beat the mascarpone, sugar and vanilla until smooth. In a 
    separate bowl, whisk double cream until it is softly whipped. 
    Fold mascarpone mix into the whipped cream, then set aside.

    Cut 8 passion fruits in half, scoop pulp into a small bowl and 
    stir in the orange juice. Slice the crusts off the brioche and 
    cut each slice into quarters.

    Lay the brioche (or cake) in the bottom of a trifle dish or 
    glass bowl. Top this with a half of the passion fruit pulp and 
    half of the mango slices, then spoon over half of the mascarpone 
    cream. Repeat the layers once more, 
    topping off with a layer of mascarpone. Use the pulp from the last 
    passion fruit to decorate. 

    The trifle will keep in the fridge for up to a day (decorate just 
    before serving).
\end{method}