\chapter{Entr\'ees}
\minitoc


\recipe[Perfect for a buffet table because they can be served at room temperature 
and can be done the day before.]{Goug\`eres Bourguignonne}
\preptime{20 minutes}
\cooktime{25 minutes}

\showit[2.5in]{img/gougere}{Perfect Goug\`eres}

\begin{ingreds}
	250ml water
    80g butter, cubed
    1 tsp fine salt
    5 large eggs
    150g plain flour, whisked
    175g gruyere or other hard cheese, grated
    ground nutmeg (optional)
    mustard powder (optional)
\end{ingreds}

\begin{method}[Preheat oven to \temp{220} (\temp{200} fan)]
    Crack four of the eggs into a jug and beat together.

    Put the water, butter and salt in a medium pan over a medium heat and bring to a simmer,
    stirring occasionally to help melt the butter.

    Take the pan off the heat and pour in the flour, stirring until it comes together into a paste. 
    
    Put back on a low heat, and stir until you have a smooth ball and the dough is starting to form 
    a layer on the base of the pan---this should take two to three minutes.

    Take off the heat and beat the dough for about five minutes, until cooled.

    Beat in the four eggs little by little, making sure each addition is well incorporated 
    before adding the next, then stir in the nutmeg, mustard powder and four-fifths of the 
    cheese.  The choux pastry is now ready for baking.

    Pipe or spoon walnut-sized blobs on to the paper, spacing them out well.

    If baking immediately, whisk together the last egg with a dash of water or milk, then brush 
    on to the buns, sprinkle with the remaining cheese and put them in the oven.

    Turn down the heat straight away to \temp{200} (\temp{180} fan) and bake for 20 minutes, 
    then pierce the side of each one with a small knife and put back in the oven for five minutes 
    to let the steam out.

    Serve warm.
\end{method}

\showit[3.5in]{img/gougere-prep}{Off the heat, beat in the eggs bit by bit, then add most of the cheese, the nutmeg and the mustard powder.}

\recipe[Perfect for vegetarian g]{Egg Salad on Salt and Vinegar Crisps}
