\chapter{Pasta}
\minitoc

\recipe[Pasta dough with a lot of 'bite' due to the increased content in Semolina.]{Egg Pasta}
\label{rec:egg-pasta}
\preptime{1 1/2 hour}
\serves{4}

\begin{ingreds}
	100g Semolina
	300g Italian '00' flour
	4 large eggs
\end{ingreds}

\begin{method}[Eggs should not come directly from the fridge.  They should be at room temperature for best results.]		
     	Add the semolina and flour into a bowl.

	Break all the eggs over the bowl and mix with the round side of the spoon to ensure all flour is hydrated.  This is a rather dry dough, don't panic when it looks like there won't be enough water to hydrate all the flour.

	Continue mixing by hand, ensuring no flour is left over and shape the dough into a ball.

	Cover with wet towel and rest for 30-45 minutes to hydrate the dough.

	Knead the dough into a smooth paste.

	Cover with cling film and rest for one hour, alternatively leave in the fridge overnight.

\end {method}

\recipe{Sfoglia all’uovo}
\label{rec:pasta-sfoglia-uovo}
\serves{2}

\begin{ingreds}
	151g "00" flour
	86g eggs (beaten)

\end{ingreds}

\begin{method}
	The classic recipe for sfoglia all’uovo uses 100 g of flour per large egg. In Bologna, sfoglini eyeball these 
	ingredients, making adjustments as needed until they can feel with their fingertips that the dough is perfectly 
	developed, a sign it will roll out into a proper sfoglia. What they are really feeling is a dough that is hydrated 
	and has reached the ideal balance of elasticity and extensibility.

	Remove excess egg white until total required weight is reached.  Beat the eggs.

	Sift the flour onto your work surface and make an 8 in [20 cm] diameter well in the center. 
	You should be able to see the work surface in the middle and the well’s walls should be high enough 
	to contain the eggs.

	Continue working the dough until a shaggy mass forms, 2 to 3 minutes.

	With both hands, pull the far end of the dough toward you quickly and energetically, fold it over itself, 
	then push it away from you using the heels of your palms. Rotate the dough a quarter turn and repeat the 
	kneading for 3 to 5 minutes until the dough is a compact mass. The dough will be slightly tacky.
	
	With both hands, pull the far end of the dough toward you quickly and energetically, fold it over itself, 
	then push it away from you using the heels of your palms. Rotate the dough a quarter turn and repeat 
	the kneading for 3 to 5 minutes until the dough is a compact mass. The dough will be slightly tacky.

\end{method}

\recipe{Spaghetti alle Vongole (Napoletana)}
\label{rec:pasta-spaghetti-vongole-napoli}
\preptime{min 5 hours}
\cooktime{1/2 hour}
\serves{4}

\begin{ingreds}
	400g Spaghetti
	1kg Clams (Vongole)
	3 Garlic Cloves
	150ml Olive Oil
	250g Pomodorini del Piennolo (optional)
	Fresh Parsley (according to taste)
	Sea Salt
\end{ingreds}

\begin{method}[Soak the clams at least for 5-6 hours in (salted cold water) to remove any remaining sand.]		
     	Add the semolina and flour into a bowl.

	Heat water for boiling the spaghetti.

	Add the olive oil to a pan, slice and add the garlic, let it brown until golden (light blonde) and remove from the pan when ready.

	Slice the pomodorini in half and add with the clams to the pan cotaining the garlic oil.

	As soon as the clams open, begin to cook the pasta.

	When ready, drain the juice of the clams into a fresh pan and add the cooked pasta and swirl to coat it with the juice.

	Plate and serve.

\end {method}




