\chapter{Patisserie}
\minitoc

\recipe[Also known as PLF.  It is used in many 'vienoisseries' such as croissants or pain au chocolat]{P\^ate Lev\'ee Ferment\'ee}
\label{rec:baking-plf}
%\preptime{5 hours}
%\cooktime{30 minutes}

\begin{ingreds}
	50\% T65
	50\% Gruau
	1.8\% Sea Salt
	15\% Sugar
	4\% Fresh Yeast
	10\% Levain (optional)
	5\% Egg
	25\% Water
	25\% Milk
	50\% Beurre de Tourage
\end{ingreds}

\begin{method}[]

First weigh the flours, then the dry ingredients commencing with the salt.
Once done proceed with the liquids.

Knead for about 10 minutes (pate ferme batarde), shape into boule, cover and 
rest for 10 minutes to relax the dough.

Then shape into 20cm to 30cm rectangle.

Cover and cool in the fridge for 30 minutes.
\end {method}

\recipe[Makes 6 croissants]{Croissants}
\label{rec:baking-crossiant}
%\preptime{5 hours}
%\cooktime{30 minutes}

\begin{ingreds}
	84g T65
	84g Gruau
	3g Sea Salt
	25g Sugar
	6g Fresh Yeast
	17g Levain
	9g Egg
	42g Water
	42g Milk
	84g Beurre de Tourage
\end{ingreds}

\begin{method}[]
Proceed as for P\^ate Lev\'ee Ferment\'ee~(sec~\ref{rec:baking-plf}).

\end {method}

\recipe[Makes 6 Pains au chocolat]{Pains au Chocolat}
\label{rec:baking-pain-au-chocolat}
\preptime{5 hours}
\cooktime{14 minutes}

\begin{ingreds}
	84g T65
	84g Gruau
	3g Sea Salt
	25g Sugar
	6g Fresh Yeast
	17g Levain
	9g Egg
	42g Water
	42g Milk
	84g Beurre de Tourage
\end{ingreds}

\begin{method}[]
Proceed as for P\^ate Lev\'ee Ferment\'ee~(sec~\ref{rec:baking-plf}).

Shape the pastry as illustrated below.

Proof for 2-2.5 hours at about \temp{28}.

Cover with eggwash and bake at \temp{160} in a fan oven for approximately 14 minutes.

\showit[3.5in]{img/pain-au-chocolat-layout}{Layout the dough to fit the cocolat batons}

\showit[3.5in]{img/pain-au-chocolat-first-fold}{Insert the first chocolate baton and fold}

\showit[3.5in]{img/pain-au-chocolat-second-fold}{Insert the second chocolate baton and fold}

\showit[3.5in]{img/pain-au-chocolat-roll-and-close}{Roll and press to close shut}

\end {method}

\recipe[Makes one loaf of Brioche as it is taught in France for the CAP Boulanger exam.]{Brioche}
\label{rec:bread-brioche}

\begin{ingreds}
	500g Farine de Gruau (T45)
	8g salt
	5g Dry Yeast
	50g Sugar
	125g Water
	125g Eggs
	100g Butter
\end{ingreds}

\begin{method}[]
	Mix and let it double in size in a warm place (oven at \temp{30} is fine).

	Degas and partition in three and shape into a bead.

	Line a bread tin with butter, cover with cling film.
	
	Let the dough proof until it rises just towards the top end of the tin (about 15-20 minutes).

	Bake in fan oven at \temp{160} for 25 minutes.

	\showit[3.5in]{img/brioche-bead-1}{Shape 3 thin baguettes}
	\showit[3.5in]{img/brioche-bead-2}{The fold as follows}
	\showit[3.5in]{img/brioche-bead-3}{}
	\showit[3.5in]{img/brioche-bead-4}{}
	\showit[3.5in]{img/brioche-bead-5}{}
	\showit[3.5in]{img/brioche-bead-6}{Finish one end, then turn and complete opposite side.}
\end{method}

